%==============================================================================
%  resume.tex — CONTENT ONLY (the "data").
%  All styling/layout lives in cv.cls. To restyle, edit cv.cls; to change what
%  the resume says, edit only this file. Build: `tectonic resume.tex` (or CI).
%==============================================================================
\documentclass{cv}
\begin{document}

% ---- Header ------------------------------------------------------------------
\name{Shamsiddin Nabiev}
\role{Senior Software Engineer \textperiodcentered\ Java / Real-Time Data}
\contact{shamsiddin@live.ru}{linkedin.com/in/nshamsiddin}{github.com/nshamsiddin}{Dublin, Ireland}
\headline{\textbf{5+ years} building real-time, cloud-native data platforms --- Apache Flink
  stream processing on AWS, with full-stack and observability depth. Two MSc degrees
  (Software Engineering, AI).}

% ---- Skills ------------------------------------------------------------------
\section{Skills}
\skill{Languages}{Java (expert), TypeScript / JavaScript, Python, SQL, Bash}
\skill{Streaming \& Messaging}{Apache Flink (Managed Flink / KDA), Apache Kafka (MSK), Amazon Kinesis, change-data-capture, event-driven \& serverless}
\skill{Backend}{Spring Boot, Node.js, DynamoDB, MongoDB, REST APIs}
\skill{Cloud \& Infra}{AWS, Terraform (IaC), Docker, Kubernetes, Jenkins, Spinnaker, CI/CD, Linux}
\skill{Observability}{OpenTelemetry, Dynatrace, distributed tracing, metrics}
\skill{Frontend \& Testing}{React, Svelte; JUnit 5, Mockito, JaCoCo}

% ---- Experience --------------------------------------------------------------
\section{Experience}

\job{Senior Software Engineer}{Autodesk}{Apr 2026 -- Present \md Dublin}
\begin{tight}
  \item Design and operate \textbf{Apache Flink} streaming applications for a real-time \textbf{change-data-capture (CDC) data platform} on AWS (Managed Flink, \textbf{Kafka/MSK}, Kinesis), powering producer and consumer pipelines across the org.
  \item Led \textbf{full-chain distributed tracing} with \textbf{OpenTelemetry and Dynatrace}, propagating trace context through Flink operators to close observability gaps and cut incident-diagnosis time.
  \item Contribute reusable connectors, operators, and instrumentation to \textbf{shared Flink platform libraries} used across multiple producer/consumer applications.
\end{tight}

\job{Software Development Engineer}{Autodesk}{Dec 2021 -- Apr 2026 \md Dublin}
\begin{tight}
  \item Built high-throughput streaming pipelines in \textbf{Java on Apache Flink}, integrating \textbf{Kafka (MSK)} and \textbf{Amazon Kinesis} for real-time change-data-capture and delivery.
  \item Authored \textbf{Terraform} infrastructure-as-code for Managed Flink and Kafka; owned \textbf{CI/CD} via Jenkins, Spinnaker, Docker, and an internal Kubernetes platform.
  \item Developed a \textbf{Spring Boot control-plane service} orchestrating Kafka resource provisioning (backed by DynamoDB), plus event-driven \textbf{Node.js} services and \textbf{React/TypeScript} front-ends.
  \item Diagnosed and fixed production issues in \textbf{stateful streaming jobs} (serialization, checkpointing, performance); maintained rigorous test coverage with JUnit, Mockito, and JaCoCo.
\end{tight}

\job{Software Engineer Intern}{Autodesk}{Mar 2021 -- Nov 2021 \md Dublin}
\begin{tight}
  \item Built full-stack features with \textbf{Java, Spring Boot, Node.js, React, and Svelte}; created modular Node.js services and used Docker and Jenkins for streamlined delivery.
\end{tight}

\job{Software Developer}{VEON}{Aug 2018 -- Aug 2019 \md Tashkent}
\begin{tight}
  \item Built \textbf{microservices and full-stack applications} with Node.js, Spring Boot, and MongoDB, collaborating cross-functionally on design, implementation, and integration.
\end{tight}

\job{Data Platforms \& Billing Systems}{VEON}{Nov 2015 -- Jul 2018 \md Tashkent}
\begin{tight}
  \item Delivered \textbf{big-data analytics and targeted-marketing platforms}; administered mission-critical \textbf{billing systems} with Bash, SQL, Perl, Python, and Oracle SQL on Linux, automating tasks and resolving performance issues.
\end{tight}

% ---- Education ---------------------------------------------------------------
\section{Education}
\edu{MSc, Computer Software Engineering}{Maynooth University}{2020 -- 2021}
\edu{MSc, Artificial Intelligence}{University of St Andrews}{2019 -- 2020}
\edu{BSc, Computer Engineering}{Politecnico di Torino}{2011 -- 2015}

% ---- Languages ---------------------------------------------------------------
\section{Languages}
Russian (native) \md Uzbek (native) \md English (professional working) \md Turkish (basic)

\end{document}
